---
title: "IDS_CDS_ADS"
author: "Elin Larsen"
date: "10/05/2018"
output: html_document
#runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, echo=TRUE, warning=FALSE, message=FALSE)
source("../util.R")
```

###Paths to modify
```{r paths}
path_to_CDI="/Users/elinlarsen/GoogleDrive/PhD_elin/Projets/CDSwordseg_Pipeline/CDI/english/"
res='/Users/elinlarsen/GoogleDrive/PhD_elin/Projets/CDSwordSeg_Pipeline/results/'
path_to_figures="/Users/elinlarsen/GoogleDrive/PhD_elin/our_papers/CogSci2018/figures/mai2018/"

#depends on the data architecture 
res_brent=paste(res, 'Brent/full_corpus', sep='/')
res_providence=paste(res, 'Providence/full_corpus', sep='/')
res_buckeye=paste(res, 'buckeye', sep='/')
```


###Load data frame containing word segmentation algorithm results and CDI data CLEAN
Look at the CDI_WordSegALgo_dataframe to know how this data have been merged 

```{r load_cdi_algo_data}
load(file = paste(res, "/braginsky_cdi_algo_combined.RData",sep=""), envir = globalenv())
# DATA is created
```

### ALGOS parameters
```{r}
algos=c('tp/relativeforward', 'tp/absoluteforward', 'tp/relativebackward', 'tp/absolutebackward','dibs','puddle','ag')
unit=c("phoneme", "syllable")
Asyll=paste(algos,"syllable", sep="/")
Aph=paste(algos,"phoneme", sep="/")
AU=c(Asyll, Aph)
AU_g=list.append(AU,"gold")
```

***Check number of CDI words per algos***
```{r nb_types}
for (a in AU_g)
{ 
  X<-DATA%>%
  filter(au==a)%>%
  group_by(uni_lemma, algos)%>%
  n_groups()
  print(paste(a, X, sep= ": "))
  }
```

###Model parameters
```{r}
AGES_comp=seq(8,18)
AGES_prod=seq(8,30)
CORPUS=c("brent", "providence", "buckeye")
MEASURE=c( 'understands')
if(MEASURE=="produces"){AGES=AGES_prod} else(AGES=AGES_comp)
AU_g=list.append(AU,"gold")
G=c("gold")
```

##Linear models

### by corpus-measure-algo-unit-age

```{r R2} 
# in linear_models.R
R2_comp=R2_by_parameters(DATA, seq(8,18), AG_g, CORPUS, "understands")
R2_prod=R2_by_parameters(DATA, seq(8,30), AG_g, CORPUS, "produces")
```


Saving results
```{r saving_results}
#write.table(R2_comp, paste(res, "/R2_eng_all_corpus_comprehension_BraginskyCDIData.csv", sep=""), na = "NA", append = FALSE, col.names = TRUE, sep="\t", row.names = FALSE)

#write.table(R2_prod, paste(res, "/R2_eng_all_corpus_production_BraginskyCDIData.csv", sep=""), na = "NA", append = FALSE, col.names = TRUE, sep="\t", row.names = FALSE)

```


Visualising results
```{r vis, fig.width=20, fig.height=12}
ggplot(R2_comp%>%filter(au%in% c("gold","tp/relativeforward/syllable",
                                          "tp/relativebackward/syllable","ag/syllable")), aes(as.factor(age), R2, colour=au, shape=corpus))+
  geom_point(size=4, alpha=0.9) +
  facet_grid(. ~ corpus)+
  theme_bw(base_size=22) 

ggplot(R2_prod%>%filter(au%in% c("gold","tp/relativeforward/syllable", "tp/relativebackward/syllable", "ag/syllable"))
       , aes(as.factor(age), R2, colour=au, shape=corpus))+
  geom_point(size=4, alpha=0.9) +
  facet_grid( ~ corpus)+
  theme_bw(base_size=22) 

```


###LM
Let's check results from IS paper : corpus==brent, measure==understands, age==13

```{r lmer_IS}
AGE=13
MEASURE="understands"
CORPUS="brent"
sub<-DATA%>%filter(age==AGE, measure==MEASURE, corpus==CORPUS)
sub$au=factor(sub$au)
sub$au=relevel(sub$au,"gold")

m0 <- lm(prop ~ log(count+1)+ log(count+1):au, sub)
summary(m0)
plot_model(m0, type="std",  sort.est = TRUE, show.values = TRUE, value.offset = .3, axis.lim = c(-0.5, 0.5))
```


Let's for each algorithm compare it predictive power to the gold
```{r pairwise_algo, echo=FALSE}
for (a in AU)
{ 
  included=c(a, "gold")
  fit1=lm(prop~log(count+1) + log(count+1):au ,data=sub,subset=c(au %in% included))
  #print(summary(fit1))
}
```


Only TPs RF with syllable
```{r}
pair=c("tp/relativeforward/syllable", "gold", "ag/syllable")
m1=lm(prop~log(count+1) + log(count+1):au ,data=sub,subset=c(au %in% pair))
summary(m1)
plot_model(m1, type="std", sort.est = TRUE, show.values = TRUE, value.offset = .3, axis.lim=c(0.5,0.5))
```


Look at the evoluation of age for all algorithms : only TP RF syllable has 1. an effect > 0.1, that is 2. significant
```{r lmer_age}
sub<-DATA%>%filter(measure==MEASURE, corpus==CORPUS)
sub$au=factor(sub$au)
sub$au=relevel(sub$au,"gold")

m2 <- lm(prop ~ log(count+1)*age+ log(count+1):au:age, sub)
summary(m2)
plot_model(m2, type="std", sort.est = TRUE, show.values = TRUE, axis.lim=as.vector(c(0,0.5)))

#plotting interaction between age and algorithm-unit pair
#plot_model(m2, type = "int", terms = c("age", "au")) # not working !!!
```


Restriction to TP-RF syllable and gold
```{r lmer-age}
included=c("tp/relativeforward/syllable", "gold", "ag/syllable")
sub<-DATA%>%filter(measure==MEASURE, corpus==CORPUS, au %in% included)
sub$au=factor(sub$au)
sub$au=relevel(sub$au,"gold")

m2_tp <- lm(prop ~ age+ log(count+1):age+ log(count+1):au:age, sub)
#m2_tp <- lm(prop ~ age + log():age+ log(freq_smoothed):au:age, sub) 
summary(m2_tp)
plot_model(m2_tp, type="std", sort.est = TRUE, show.values = TRUE, axis.lim=as.vector(c(0,1)))
```

Weird fact :  the p-value with count is clearly not the same than with freq_smoothed!

```{r interaction_algo, fig.width=12, fig.height=9}
if(MEASURE=="understands"){task="comprehension"}else{task="production"}
m=lm(prop~ log_freq*as.factor(age)*au, sub)

 plot_model(m, type="pred", terms=c("log_freq", "au", "age"), title=paste("Predicted values of proportion of infants",task, "across ages in", CORPUS, "corpus", sep=" "))
```


##Let's for each algorithm compare it predictive power to the gold with age evolution
```{r pairwise}
for (a in AU)
{ 
  included=c(a, "gold")
  #fit2=lm(prop~ age+ log(count+1):age + log(count+1):au:age ,data=sub,subset=c(au %in% included))
  #print(summary(fit2))
}
```

***Now corpus="brent", measure="produces", algos='TP-RF-syll'***
```{r}
MEASURE="produces"
CORPUS="brent"
included=c("tp/relativeforward/syllable", "gold")
sub<-DATA%>%filter(measure==MEASURE, corpus==CORPUS, au %in% included)
sub$au=factor(sub$au)
sub$au=relevel(sub$au,"gold")

m_b_prod <- lm(prop ~ age + log(count+1):age+ log(count+1):au:age, sub)
summary(m_b_prod)
plot_model(m_b_prod, type="std",  sort.est = TRUE, show.values = TRUE, value.offset = .3)
```

***Now corpus="providence", measure="understands", algos='TP-RF-syll'***
```{r}
MEASURE="understands"
CORPUS="providence"
included=c("tp/relativeforward/syllable", "gold")
sub<-DATA%>%filter(measure==MEASURE, corpus==CORPUS, au %in% included)
sub$au=factor(sub$au)
sub$au=relevel(sub$au,"gold")

m_b_prod <- lm(prop ~ age + log(count+1):age+ log(count+1):au:age, sub)
summary(m_b_prod)
plot_model(m_b_prod, type="std",  sort.est = TRUE, show.values = TRUE, value.offset = .3)
```


***Now corpus="providence", measure="produces", algos='TP-RF-syll'***
```{r}
MEASURE="produces"
CORPUS="providence"
included=c("tp/relativeforward/syllable", "gold")
sub<-DATA%>%filter(measure==MEASURE, corpus==CORPUS, au %in% included)
sub$au=factor(sub$au)
sub$au=relevel(sub$au,"gold")

m_b_prod <- lm(prop ~ age + log(count+1):age+ log(count+1):au:age, sub)
summary(m_b_prod)
plot_model(m_b_prod, type="std",  sort.est = TRUE, show.values = TRUE, value.offset = .3)
```


***Now corpus="buckeye", measure="understands", algos='TP-RF-syll'***
```{r}
MEASURE="understands"
CORPUS="buckeye"
included=c("tp/relativeforward/syllable", "gold")
sub<-DATA%>%filter(measure==MEASURE, corpus==CORPUS, au %in% included)
sub$au=factor(sub$au)
sub$au=relevel(sub$au,"gold")

m_b_prod <- lm(prop ~ age + log(count+1):age+ log(count+1):au:age, sub)
summary(m_b_prod)
plot_model(m_b_prod, type="std",  sort.est = TRUE, show.values = TRUE, value.offset = .3)
```


***Now corpus="buckeye", measure="produces", algos='TP-RF-syll'***
```{r}
MEASURE="produces"
CORPUS="buckeye"
included=c("tp/relativeforward/syllable", "gold")
sub<-DATA%>%filter(measure==MEASURE, corpus==CORPUS, au %in% included)
sub$au=factor(sub$au)
sub$au=relevel(sub$au,"gold")

m_b_prod <- lm(prop ~ age + log(count+1):age+ log(count+1):au:age, sub)
summary(m_b_prod)
plot_model(m_b_prod, type="std",  sort.est = TRUE, show.values = TRUE, value.offset = .3)
```


##Linear mixed effect model 
**One big model : corpus and measure included and interacting with algorithm-unit and log frequency**

***Let's fix age***
```{r lmer_big}
AGE=13
included=c("gold", "tp/relativeforward/syllable")
x<-DATA%>%filter(age==AGE, au %in% included)
x$au=as.factor(x$au)
x$corpus=as.factor(x$corpus)
x$measure=as.factor(x$measure)
x$au=relevel(x$au,"gold")
x$corpus=relevel(x$corpus,"buckeye")
x$measure=relevel(x$measure, "understands")

m3 <- lmer(prop ~ log(freq_smoothed)+ log(freq_smoothed):au:corpus:measure +(1 + log(freq_smoothed)|uni_lemma),  x)
summary(m3)
#plot_model(m3, type = "std", sort.est = TRUE, show.values = TRUE) # not working !!!!
```


Interaction between corpus and measure and algorithm by 18 month
```{r interaction-AU-corpus-prod, fig.width=12, fig.height=9}
MEASURE="produces"
AGE=25
if(MEASURE=="understands"){task="comprehension"}else{task="production"}
included=c("gold", "tp/relativeforward/syllable", "ag/syllable")
x<-DATA%>%filter(age==AGE, au %in% included, measure==MEASURE)

m <- lm(prop ~ log_count*au*corpus, x)

plot_model(m, type="pred", terms=c("log_count", "au", "corpus"), title=paste("Predicted values for proportion of", AGE, "mo infants", task, sep=" "))
```

```{r interaction-AU-corpus-comp, fig.width=12, fig.height=9}
MEASURE="understands"
AGE=16
if(MEASURE=="understands"){task="comprehension"}else{task="production"}
included=c("gold", "tp/relativeforward/syllable",  "ag/syllable")
x<-DATA%>%filter(age==AGE, au %in% included, measure==MEASURE)
m <- lm(prop ~ log_count*au*corpus, x)

plot_model(m, type="pred", terms=c("log_count", "au", "corpus"), title=paste("Predicted values for proportion of", AGE, "mo infants", task, sep=" "))

```


Interesting right ? It seems (though I would love to properly test statistically and have the statistical power to do so) that TP-RF syllable prediction are clearly separated for comprehension for the Brent and Providnece corpus but not at all for the buckeye corpus. 
For production at 18 mo prediction differences are not so clear : so let's look at the evolution of these predictions across ages. 


***With age as a main effect, which slopes depends ***
The thing is : the comprehension measure is only available from 8 to 18 mo, while the production one is available from 8 to 30 mo.
```{r lmer_full_model}

included=c("gold", "tp/relativeforward/syllable")
x<-DATA%>%filter(au %in% included)
x$au=as.factor(x$au)
x$corpus=as.factor(x$corpus)
x$measure=as.factor(x$measure)

x$au=relevel(x$au,"gold")
x$corpus=relevel(x$corpus,"buckeye")
x$measure=relevel(x$measure, "understands")
m4 <- lmer(prop ~ age*log(freq_smoothed)+ log(freq_smoothed):au:corpus:measure +(1+age+ log(freq_smoothed)|uni_lemma),  x)
summary(m4)
```

**Checking model assumptions : Arghh;...**
```{r assumptions}
plot_model(m0, type="diag")
plot_model(m1, type="diag")
plot_model(m2, type="diag")
plot_model(m3, type="diag")
```