---
title: "WordSegAnalysis"
author: "Elin Larsen"
date: "08/05/2018"
output: html_document 
runtime: shiny
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
knitr::opts_chunk$set(fig.width=22, fig.height=40, echo=FALSE, warning=FALSE, message=FALSE) 

source("../util.R")
```


***Parameters to fill***
```{r}
path_to_CDI="/Users/elinlarsen/GoogleDrive/PhD_elin/Projets/CDSwordseg_Pipeline/CDI/english/"

path_res='~/GoogleDrive/PhD_elin/Projets/CDSwordSeg_Pipeline/results/res-brent-CDS/full_corpus/'
path_ortho="~/GoogleDrive/PhD_elin/Projets/CDSwordSeg_Pipeline/recipes/childes/data/Brent/ortholines.txt"

path_to_figures="/Users/elinlarsen/GoogleDrive/PhD_elin/our_papers/CogSci2018/figures/mai2018/"
save=TRUE # whether or not to save figures in path_to_figures
FORM="WG_comprehension"
AGE=13
UNIT="syllable"
```

***Load reshaped CDI database with CDI_Data.Rmd script***
```{r, echo=FALSE, message=FALSE, results='asis'}
 destfile= path_to_CDI_reshape=paste(path_to_CDI, "/Prop_all_forms_reshaped.csv", sep="")
 scriptfile <- "/Users/elinlarsen/GoogleDrive/PhD_elin/Projets/WordSegComprehension/wordsegcomp/CDI/reshape_CDI_Data.R"
 if (!file.exists(destfile))
   {
    source(scriptfile)
    print("running reshape_CDI_Data.R")
 }
d_prop =read_delim(destfile, "\t", escape_double = FALSE, trim_ws = TRUE)


knitr::kable(head(d_prop), format = "html")%>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Analysis of word segmentation algorithms output 

This R Markdown document is aimed at analyzing word segmentation algorithms output relatively to reported infant word comprehension. 

###PART 1: data processing

**Number of occurrence of wordS correctly segmented by each algo**
```{r, echo=FALSE, message=FALSE}
algos=c('TPs','DiBs','PUDDLE','AGu', 'gold')

freq_algos=read_algorithms_results(algos, path_res, "brent")

knitr::kable(head(freq_algos), format = "html")%>%
kable_styling(bootstrap_options = c("striped", "hover"))
```

**Final dataset containging all variables without CDI info**
```{r,  echo=FALSE, message=FALSE}

dat_all_forms=merge(d_prop, freq_algos, by="Type")
dat_all_forms$corpus=rep("Brent", nrow(dat_all_forms))

write.table(dat_all_forms, paste(path_res, "/res_algos_cdi_reshaped.csv", sep=""), na = "NA", append = FALSE, col.names = TRUE, sep="\t", row.names = FALSE)


dat<-dat_all_forms%>%
  filter(form==FORM)

dat_age<- dat%>%
  filter(age==AGE)

dat_age_unit<-dat%>%
  filter(age==AGE, unit==UNIT)

dat_unit<-dat%>%
  filter(unit==UNIT)

knitr::kable(head(dat), format = "html")%>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

------

## PART 2 : Visualizing the data

***select randomly X word types for different lexical classes and look at the evolution of understanding over age***
```{r,echo=FALSE, results='hide',message=FALSE, fig.width=10,fig.height=9}
#proportion_for_sampled_types(dat, c( "pronouns"), NA,FALSE, legend_name="type" )
#proportion_for_sampled_types(dat, c("adverbs", "prepositions", "pronouns", "determiners", "wh-"), NA,FALSE )
#proportion_for_sampled_types(dat, c("nouns", "adjectives", "verbs", "exclamation"), c(20, 20, 20, 7),TRUE)  

```

***select randomly X word types for different lexical open_close and look at the evolution of understanding over age***
```{r,echo=FALSE, results='hide', message=FALSE, fig.width=10,fig.height=9}
#proportion_for_sampled_types(dat, c("function", "content"), c(20,20), TRUE, "lex" )
```


***Box plots***

```{r eruptions, echo=FALSE, cache=FALSE}
inputPanel(
  sliderInput("ages", label = "Ages (month)",
              min = 8, max = 30, value = 13, step = 1)
)

renderPlot({
  d<-dat_all_forms%>%
    filter(age==input$ages, open_close  %in% c("function", "content"))

  qplot(length, prop, facets = form ~ open_close, 
      colour = open_close, geom = "boxplot", data = d)+
  labs(title='Proportion of reported infant comprehension/production at 13 mo', y="Proportion ", x="Word length")+
   theme_linedraw(base_size = 12)
})
```



***Evolution with age of the effect of word length and lexical classes***
```{r, echo=FALSE, cache=FALSE}
inputPanel(
  selectInput("forms", label = "Vocabulary forms",
              choices = c("WG_comprehension", "WG_production", "WS_production"), selected = "WG_comprehension")
)

renderPlot({
  d<-dat_all_forms%>%
    filter(form==input$forms, open_close  %in% c("function", "content"))
  
  ggplot(data=d, aes(x=length, y=prop)) + 
  geom_boxplot(aes(fill=age)) +
  facet_grid(. ~ age)+
  labs(title="", x="Length", y="Proportion of reported comprehension")

})
```

```{r, cache=FALSE, echo=FALSE,message=FALSE}
inputPanel(
  selectInput("forms", label = "Vocabulary forms",
              choices = c("WG_comprehension", "WG_production", "WS_production"), selected = "WG_comprehension"),
  
  selectInput("factors", label = "Linguistic factors",
              choices = c("length", "open_close"), selected = "length")
)

renderPlot({
  d<-dat_all_forms%>%
    filter(form==input$forms, open_close  %in% c("function", "content"))
  
if (input$factors=="length")
{
  x=d$length
}
else{x=d$open_close}
 ggplot(d, aes(x, y = prop, colour = input$factors)) +
  geom_boxplot(aes(fill=input$factors)) +
  facet_grid(. ~ age)+
  labs(title="Proportion of reported comprehension/production across ages", x="Ages", y="Proportion ")+
  theme_linedraw(base_size = 12)
})
```

```{r,  echo=FALSE ,message=FALSE, cache=FALSE}
inputPanel(
  selectInput("forms", label = "Vocabulary forms",
              choices = c("WG_comprehension", "WG_production", "WS_production"), selected = "WG_comprehension"),
  
  selectInput("lex", label = "Lexical class",
              choices = c("adverbs", "prepositions", "pronouns", "determiners", "wh-", "nouns","adjectives", "verbs"),               selected = "nouns")
)

renderPlot({
d=dat_all_forms%>%
  filter(form==input$forms, lc==input$lex)

ggplot(data=d, aes(x=lc, y=prop)) + 
  geom_boxplot(aes(fill=lc)) +
  facet_wrap( ~ age)+
  labs(title="", x="Lexical category", y="Proportion of reported comprehension/production")
})
```

-----

## PART 3 : Linear regression

### Linear models for each algorithm-pair unit for each age in the CDI

***Figure of R2 with raw CDI reports***
```{r , echo=FALSE, cache=FALSE}
inputPanel(
  selectInput("forms", label = "Vocabulary forms",
              choices = c("WG_comprehension", "WG_production", "WS_production"), selected = "WG_comprehension"),
  
 inputPanel(
  sliderInput("ages", label = "Ages (month)",
              min = 8, max = 30, value = 13, step = 1)
 )
)

renderPlot({
  d<-dat_all_forms%>%
    filter(form==input$forms, open_close  %in% c("function", "content"), age==input$ages)
  
  ## !!!! replace c(13) by c(input$ages)
  R2=Linear_model(d, c(input$ages), c('TPs', 'PUDDLE', 'DiBs', 'AGu', 'gold'),c("syllable", "phoneme"))
  R2_gold<-R2%>%filter(algo=="gold")
  R2_algos<-R2%>%filter(algo %in% c('TPs', 'PUDDLE', 'DiBs', 'AGu'))

ggplot(R2_algos, aes(x = algo, y = R2, fill=algo)) +
  geom_bar(position="dodge", stat="identity", show.legend=TRUE)+
  geom_abline(data=R2_gold, aes(slope=0, intercept=R2))+
  geom_text(data=R2_algos, aes(label=nbtokens), vjust=2, color="black", size=6)+
  facet_grid( ~ unit)+
  theme_light(base_size = 14)+
  labs(title="", x="", y="Coefficient of determination R2")
  
})
```


```{r , echo=FALSE, cache=FALSE}
inputPanel(
  selectInput("forms", label = "Vocabulary forms",
              choices = c("WG_comprehension", "WG_production", "WS_production"), selected = "WG_comprehension")
  )


renderPlot({
  d<-dat_all_forms%>%
    filter(form==input$forms, open_close  %in% c("function", "content"))
  
  if(input$forms %in% c("WG_comprehension", "WG_production"))
  {AGES=c(8:18)}
  else{AGES=c(16:30)}
  
  R2=Linear_model(d,AGES, c('TPs', 'PUDDLE', 'DiBs', 'AGu', 'gold'),c("syllable", "phoneme"))

#if (save==TRUE)
#{png( paste(path_to_figures, "R2_over_ages.png", sep="") ,width=4500,height=3000, res=200 )}
  R2_gold<-R2%>%filter(algo=="gold")
  R2_algos<-R2%>%filter(algo %in% c('TPs', 'PUDDLE', 'DiBs', 'AGu'))
  R2_TPs<-R2%>%filter(algo %in% c('TPs'))
  R2_DiBS<-R2%>%filter(algo %in% c('DiBs'))
  R2_PUDDLE<-R2%>%filter(algo %in% c('PUDDLE'))
  R2_AGu<-R2%>%filter(algo %in% c('AGu'))
  
  ggplot(data=R2, aes(x = age, y = R2, colour=algo, group=unit)) +
    geom_point()+
    geom_line(data=R2_gold, aes(age, R2, colour=algo))+
    geom_line(data=R2_TPs, aes(age, R2, colour=algo, group=unit))+
    geom_line(data=R2_DiBS, aes(age, R2, colour=algo, group=unit))+
    geom_line(data=R2_PUDDLE, aes(age, R2, colour=algo, group=unit))+
    geom_line(data=R2_AGu, aes(age, R2, colour=algo, group=unit))+
    facet_grid(. ~ unit)+
    labs(title="", x="Ages (month)", y="Coefficient of determination R2")+
    theme_linedraw(base_size = 16)+
    theme(legend.position="top")+
    scale_x_discrete(limit = c(8:18), labels = c("8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18"))
  
})
```




***Function versus content words***
```{r, cache=FALSE, echo=FALSE, message=FALSE, fig.width=10,fig.height=9}

inputPanel(
  selectInput("forms", label = "Vocabulary forms",
              choices = c("WG_comprehension", "WG_production", "WS_production"), selected = "WG_comprehension"),
  
  sliderInput("ages", label = "Ages (month)",
              min = 8, max = 30, value = 13, step = 1),
  
   selectInput("factors", label = "Linguistic factors",
              choices = c("length", "open_close"), selected = "length")
  
  )

renderPlot({
  d<-dat_all_forms%>%
    filter(form==input$forms, open_close  %in% c("function", "content"))
  
  if(input$forms %in% c("WG_comprehension", "WG_production"))
  {AGES=c(8:18)}
  else{AGES=c(16:30)}
  
  if(input$factors=="open_close")
  {FACTORS=c("function", "content")}
  else{FACTORS=c("M", "P")}


    R2=Linear_model_by_group(dat, c(input$ages), c('TPs', 'PUDDLE', 'DiBs', 'AGu', 'gold'),c("syllable", "phoneme"), group1= input$factors, var_group1 = FACTORS)
    R2_gold<-R2%>%filter(algo=="gold")
    R2_algos<-R2%>%filter(algo %in% c('TPs', 'PUDDLE', 'DiBs', 'AGu'))
    
    #if (save==TRUE)
    #{png(paste(path_to_figures, "/R2_13mo_FunctionContent_nbtokens.png", sep=""),width=2500,height=2500, res=200 )}
    
    ggplot(R2_algos, aes(x = algo, y = R2, fill=algo)) +
      geom_bar(position="dodge", stat="identity", show.legend=TRUE)+
      geom_abline(data=R2_gold, aes(slope=0, intercept=R2))+
      geom_text(data=R2_algos, aes(label=nbtokens), vjust=2, color="black", size=6)+
      facet_grid(group1 ~ unit)+
      theme_linedraw(base_size = 16)+
      scale_y_continuous(limits = c(0, 0.35))+
      theme(legend.position="top")+
      labs(title="", x="", y="R2")

})
```


***Mono verus polysyllabic words***
```{r, cache=FALSE, echo=FALSE, message=FALSE, fig.width=10,fig.height=9}
R2_length=Linear_model_by_group(dat, c(13), c('TPs', 'PUDDLE', 'AGu', 'gold', 'DiBs'),c("syllable", "phoneme"), group1= "length", var_group1 = c("M", "P") )
R2_length_gold<-R2_length%>%filter(algo=="gold")
R2_length_algos<-R2_length%>%filter(algo %in% c('TPs', 'PUDDLE', 'DiBs', 'AGu'))

if (save==TRUE)
{png(paste(path_to_figures, "/R2_13mo_MP_nbtokens.png", sep=""),width=2500,height=2500, res=200 )}

ggplot(R2_length_algos, aes(x = algo, y = R2, fill=algo)) +
  geom_bar(position="dodge", stat="identity",show.legend=TRUE)+
  geom_abline(data=R2_length_gold, aes(slope=0, intercept=R2))+
  geom_text(data=R2_length_algos, aes(label=nbtokens), vjust=-1, color="black", size=6)+
  facet_grid(group1 ~ unit)+
  theme_linedraw(base_size = 22)+
  scale_y_continuous(limits = c(0, 0.35))+
  theme(legend.position="top")+
  labs(title="", x="", y="Coefficient of determination R2")
dev.off()
# Note : DiBS with syllable has no polysyllabic words : R2=0 by default
```


***Interaction length open/close class ***
**** For TPs across ages ****
```{r}
R2=Linear_model_by_group(dat, c(8:18), c('TPs', 'PUDDLE', 'AGu', 'gold', 'DiBs'),c("syllable", "phoneme"), group1= "length", var_group1 = c("M", "P"),group2= "open_close", var_group2 = c("function", "content") )
```


```{r}
#R2=mean_R2_over_CDI_reports(d_comprehension, data_algo, 66, c(8:18), 10, c('TPs', 'PUDDLE', 'DiBs', 'AGu', 'gold'),c("syllable", "phoneme"))
```

```{r}
R2_g<-R2%>%filter(algo=="gold" )
R2_algos<-R2%>%filter(algo %in% c('TPs', 'PUDDLE', 'AGu', 'DiBs'))
R2_TP<-R2%>%filter(algo %in% c('TPs', 'gold'), unit=="syllable")

if (save==TRUE)
{png(paste(path_to_figures, "/R2_TPs_MP_FC_phoneme_syllable_nbtokens.png", sep=""),width=2500,height=2500, res=200 )}

ggplot(R2_TP, aes(x = age, y = R2, fill=algo)) +
  geom_bar(position="dodge", stat="identity")+
  #geom_abline(data=R2_g, aes(slope=0, intercept=R2))+
  facet_grid(group1 ~ group2)+
  #geom_text(data=R2_TP, aes(label=nbtokens), vjust=0, color="black", size=6, position = position_dodge(0.9))+
  theme_linedraw(base_size = 22)+
  scale_y_continuous(limits = c(0, 0.38))+
  theme(legend.position="top")+
  labs(title="", x="Age (month)", y="Coefficient of determination R2")+
  scale_x_discrete(limit = c(8:18), labels = c("8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18"))
dev.off()
```


***For all algo at one age ***
```{r}
R2=Linear_model_by_group(dat, c(13), c('TPs', 'PUDDLE', 'AGu', 'gold', 'DiBs'),c("syllable", "phoneme"), group1= "length", var_group1 = c("M", "P"),group2= "open_close", var_group2 = c("function", "content") )
R2_g<-R2%>%filter(algo=="gold" )
R2_algos<-R2%>%filter(algo %in% c('TPs', 'PUDDLE', 'AGu', 'DiBs'))
R2_TP<-R2%>%filter(algo %in% c('TPs', 'gold'), unit=="syllable")

if (save==TRUE)
{png(paste(path_to_figures, "/R2_13mo_MP_FC_phoneme_syllable_nbtokens.png", sep=""),width=2500,height=2500, res=200 )}

ggplot(R2_algos, aes(x = algo, y = R2, fill=unit)) +
  geom_bar(position="dodge", stat="identity")+
  geom_abline(data=R2_g, aes(slope=0, intercept=R2))+
  facet_grid(group1 ~ group2)+
  geom_text(data=R2_algos, aes(label=nbtokens), vjust=0, color="black", size=6, position = position_dodge(0.9))+
  theme_linedraw(base_size = 24)+
  scale_y_continuous(limits = c(0, 0.6))+
  theme(legend.position="top")+
  labs(title="", x="", y="Coefficient of determination R2")
dev.off()
```

***Lexical classes***
```{r, echo=FALSE, message=FALSE, fig.width=10,fig.height=9}
R2_lexclasses=Linear_model_by_group(dat, c(13), c('TPs', 'PUDDLE', 'DiBs', 'AGu', 'gold'),c("syllable", "phoneme"), group1= "lc", var_group1 = c("nouns", "adjectives", "verbs","exclamation", "adverbs", "prepositions", "pronouns", "determiners", "wh-"))

ggplot(R2_lexclasses, aes(x = algo, y = R2, fill=algo)) +
  geom_bar(position="dodge", stat="identity")+
  facet_grid(group1 ~ unit)
```

------

## Linear mixed effect model

***Assumptions***
```{r}
  
d_gold=dat_age_unit%>%filter(algos=="gold")
hist(d_gold$prop)

qqnorm(d_gold$prop, main="QQplot")  
qqline(d_gold$prop)  

#skeweness of the distribution
skewness(d_gold$prop)

# number of words per algo-syllable : 
#design is not balanced (i.e. some groups have more samples) => normal ANOVA cannot be used, 
tapply(dat_age_unit$prop, INDEX=dat_age_unit$algos, FUN=length)


```


***Anova with algorithm as a factor***
```{r}

m0=lm(prop~ scale(log(Freq)), data=dat_age_unit%>%filter(algos=='TPs')) 
m1=lmer(prop~  (1+log(Freq)*open_close|algos), data=dat_age_unit) # one-way anova

#TukeyHSD(m0, conf.level=0.95, which=c("open_close"))

summary(m1)
#testInteractions(m1)

```

***Fixed effect of frequency, algo and unit at 13mo***
```{r}
fit_fixed=lm(prop ~ log(Freq) + algos, dat_age_unit, REML = TRUE)
fit_0=lm(prop ~ log(Freq) ,dat_age_unit, REML = TRUE)
summary(fit_fixed)
summary(fit_0)
summary(anova(fit_0, fit_fixed))
```

***Model 0 : fixed effect of Frequency and random effect of algo-syllable at 13 mo***
```{r}
fit_random_inter=lmer(prop ~ log(Freq) + (1|algos), dat_age_unit, REML = TRUE)
fit_random_slope=lmer(prop ~ log(Freq)  +(1+ log(Freq)|algos) ,dat_age_unit, REML = TRUE)
summary(fit_random_inter)
summary(fit_random_slope)
anova(fit_random_inter, fit_random_slope)
summary(anova(fit_random_inter, fit_random_slope))
```

***Model 1 : fixed effect of Frequency and random effect of algo and ages***
```{r}
fit_random_inter=lmer(prop ~ log(Freq) + (1|algos) + (1|age), dat_unit, REML = TRUE)
fit_random_slope=lmer(prop ~ log(Freq)  +(1+ log(Freq)|algos)+(1+ log(Freq)|age),dat_unit, REML = TRUE)
summary(fit_random_inter)
summary(fit_random_slope)
anova(fit_random_inter, fit_random_slope)
summary(anova(fit_random_inter, fit_random_slope))
```


**Comparing models with anova**
```{r}

fit_length <- lmer(prop ~ log(Freq)+ +(1+log(Freq)|algos) + length , data=dat_age_unit, REML = TRUE)

fit_open_close<- lmer(prop ~ log(Freq) +(1+log(Freq)|algos) + open_close , data=dat_age_unit, REML = TRUE)

fit0=lmer(prop ~ log(Freq) +(1+log(Freq)|algos), dat_age_unit, REML = TRUE)

fit_total <- lmer(prop ~ log(Freq) +(1+log(Freq)|algos) + length* open_close, dat_age_unit, REML = TRUE)

summary(fit_length)
summary(fit_open_close)
summary(fit0)
summary(fit_total)
anova(fit0,  fit_total)
```
**Comparing models with Bayes factor**
```{r}
dat_age_unit$logFreq=log(dat_age_unit$Freq)
#bf = lmBF(formula = prop ~ logFreq + length* open_close, data = dat_age_unit%>%filter(algos=='TPs'), whichRandom = "ID", posterior = TRUE,iterations = 1000)
bf = lmBF(formula = prop ~ logFreq + length* open_close, data = dat_age_unit%>%filter(algos=='TPs'), whichRandom = "ID")
```
