---
title: "WordSegAnalysis"
author: "Elin Larsen"
date: "08/05/2018"
output: 
  html_notebook: 
    fig_caption: yes
    fig_height: 20
    fig_width: 16
runtime: shiny
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache=TRUE)
```


### Parameters to fill NOW
```{r, include=FALSE}
source("util.R")

path_to_CDI="/Users/elinlarsen/GoogleDrive/PhD_elin/Projets/CDSwordseg_Pipeline/CDI/english/"

#ALGO
path_res='~/GoogleDrive/PhD_elin/Projets/CDSwordSeg_Pipeline/results/res-brent-CDS/full_corpus/'
path_ortho="~/GoogleDrive/PhD_elin/Projets/CDSwordSeg_Pipeline/recipes/childes/data/Brent/ortholines.txt"

path_to_figures="/Users/elinlarsen/GoogleDrive/PhD_elin/our_papers/CogSci2018/figures/mai2018/"
save=TRUE # whether or not to save figures in path_to_figures


FORM="WG_comprehension"
AGE=13
UNIT="syllable"
```

### Load reshaped CDI database with CDI_Data.Rmd script
```{r, echo=FALSE, message=FALSE}
 destfile= path_to_CDI_reshape=paste(path_to_CDI, "/Prop_all_forms_reshaped.csv", sep="")
 scriptfile <- "/Users/elinlarsen/GoogleDrive/PhD_elin/Projets/WordSegComprehension/wordsegcomp/CDI/reshape_CDI_Data.R"
 if (!file.exists(destfile))
   {
    source(scriptfile)
    print("running reshape_CDI_Data.R")
 }
d_prop =read_delim(destfile, "\t", escape_double = FALSE, trim_ws = TRUE)

```

## Analysis of word segmentation algorithms output 

This R Markdown document is aimed at analyzing word segmentation algorithms output relatively to reported infant word comprehension. 

###PART 1: data processing

**Number of occurrence of wordS correctly segmented by each algo**
```{r, echo=FALSE, message=FALSE}
algos=c('TPs','DiBs','PUDDLE','AGu', 'gold')
datalist = list()
L=length(algos)
for (j in 1:L)
    { 
      algo=algos[j] #get data about algo results
      file_freq=paste(path_res, '/',algo,'/', "syllable",'/freq-words.txt', sep="")
      freq=read_delim(file=file_freq, "\t", escape_double = FALSE, trim_ws = TRUE)
      freq$unit <- "syllable"  
      freq$algos<-algo
      datalist[[j]] <- freq
}

for (j in 1:L)
    { 
      algo=algos[j] #get data about algo results
      file_freq=paste(path_res, '/',algo,'/', "phoneme",'/freq-words.txt', sep="")
      freq=read_delim(file=file_freq, "\t", escape_double = FALSE, trim_ws = TRUE)
      freq$unit <- "phoneme"  
      freq$algos<-algo
      datalist[[L+j]] <- freq
}

freq_algos <- dplyr::bind_rows(datalist)
head(freq_algos)
```

**Final dataset containging all variables without CDI info**
```{r,  echo=FALSE, message=FALSE}

dat_all_forms=merge(d_prop, freq_algos, by="Type")

dat<-dat_all_forms%>%
  filter(form==FORM)

dat_age<- dat%>%
  filter(age==AGE)

dat_age_unit<-dat%>%
  filter(age==AGE, unit==UNIT)

dat_unit<-dat%>%
  filter(unit==UNIT)


head(dat)
```

------

## PART 2 : Visualizing the data

***select randomly X word types for different lexical classes and look at the evolution of understanding over age***
```{r,echo=FALSE, results='hide',message=FALSE, fig.width=10,fig.height=9}
#proportion_for_sampled_types(dat, c( "pronouns"), NA,FALSE, legend_name="type" )
#proportion_for_sampled_types(dat, c("adverbs", "prepositions", "pronouns", "determiners", "wh-"), NA,FALSE )
#proportion_for_sampled_types(dat, c("nouns", "adjectives", "verbs", "exclamation"), c(20, 20, 20, 7),TRUE)  

```

***select randomly X word types for different lexical open_close and look at the evolution of understanding over age***
```{r,echo=FALSE, results='hide', message=FALSE, fig.width=10,fig.height=9}
#proportion_for_sampled_types(dat, c("function", "content"), c(20,20), TRUE, "lex" )
```


***Box plots***


```{r,fig.width=10,fig.height=9}
d<-dat_all_forms%>%
  filter(age==AGE, open_close  %in% c("function", "content"))

if (save==TRUE)
{png(paste(path_to_figures , "/Prop_13mo_MP_FC.png", sep=""), width=1600,height=1250, res=200)}
qplot(length, prop, facets = form ~ open_close, 
      colour = open_close, geom = "boxplot", data = d)+
  labs(title='Proportion of reported infant comprehension/production at 13 mo', y="Proportion ", x="Word length")+
   theme_linedraw(base_size = 12)

dev.off()
```


***Evolution with age of the effect of word length and lexical classes***
```{r,  echo=FALSE, results='hide',message=FALSE, fig.width=10,fig.height=9}

ggplot(data=dat, aes(x=length, y=prop)) + 
  geom_boxplot(aes(fill=age)) +
  facet_grid(. ~ age)+
  labs(title="", x="Length", y="Proportion of reported comprehension")

d_fn=dat%>%
  filter(lc %in% c("adverbs", "prepositions", "pronouns", "determiners", "wh-"))
ggplot(data=d_fn, aes(x=lc, y=prop)) + 
  geom_boxplot(aes(fill=lc)) +
  facet_grid(. ~ age)+
  labs(title="", x="Lexical category", y="Proportion of reported comprehension")

d_cn=dat%>%
  filter(lc %in% c("nouns", "adjectives", "verbs"))
ggplot(data=d_cn, aes(x=lc, y=prop)) + 
  geom_boxplot(aes(fill=lc)) +
  facet_grid(. ~ age)+
  labs(title="", x="lexical category", y="Proportion of reported comprehension")

if (save==TRUE)
{png(paste(path_to_figures ,"/Prop_over_ages_content_function.png", sep=""),width=1600,height=1250, res=200 )}

d=dat%>%
  filter(open_close %in% c("function", "content"))
ggplot(d, aes(x = open_close, y = prop, colour = open_close)) +
  geom_boxplot(aes(fill=open_close)) +
  facet_grid(. ~ age)+
  labs(title="Proportion of reported comprehension across ages", x="Ages", y="Proportion ")+
  theme_linedraw(base_size = 30)
  
dev.off()
```

```{r,  echo=FALSE, results='hide',message=FALSE, fig.width=10,fig.height=9}
if (save==TRUE)
{png(paste(path_to_figures, "/Prop_over_ages_M_P.png", sep=""),width=1600,height=1250, res=200 )}
d=dat%>%
  filter(length %in% c("M", "P"))
ggplot(d, aes(x = length, y = prop, colour = length)) +
  geom_boxplot(aes(fill=length)) +
  facet_grid(. ~ age)+
  labs(title="Proportion of reported comprehension across ages", x="Ages", y="Proportion")+
  theme_linedraw(base_size = 30)
dev.off()

```

------

## PART 3 : Linear regression

### Linear models for each algorithm-pair unit for each age in the CDI

***Figure of R2 with  sample CDI reports***
```{r, echo=FALSE, message=FALSE}
#R2=mean_R2_over_CDI_reports(d_comprehension, data_algo, 66, c(8:18), 10, c('TPs', 'PUDDLE', 'DiBs', 'AGu', 'gold'),c("syllable", "phoneme"))

R2=Linear_model(dat,c(8:18), c('TPs', 'PUDDLE', 'DiBs', 'AGu', 'gold'),c("syllable", "phoneme"))

if (save==TRUE)
{png( paste(path_to_figures, "R2_over_ages.png", sep="") ,width=4500,height=3000, res=200 )}
R2_gold<-R2%>%filter(algo=="gold")
R2_algos<-R2%>%filter(algo %in% c('TPs', 'PUDDLE', 'DiBs', 'AGu'))
R2_TPs<-R2%>%filter(algo %in% c('TPs'))
R2_DiBS<-R2%>%filter(algo %in% c('DiBs'))
R2_PUDDLE<-R2%>%filter(algo %in% c('PUDDLE'))
R2_AGu<-R2%>%filter(algo %in% c('AGu'))

ggplot(data=R2, aes(x = age, y = R2, colour=algo, group=unit)) +
  geom_point()+
  geom_line(data=R2_gold, aes(age, R2, colour=algo))+
  geom_line(data=R2_TPs, aes(age, R2, colour=algo, group=unit))+
  geom_line(data=R2_DiBS, aes(age, R2, colour=algo, group=unit))+
  geom_line(data=R2_PUDDLE, aes(age, R2, colour=algo, group=unit))+
  geom_line(data=R2_AGu, aes(age, R2, colour=algo, group=unit))+
  facet_grid(. ~ unit)+
  labs(title="", x="Ages (month)", y="Coefficient of determination R2")+
  theme_linedraw(base_size = 30)+
  theme(legend.position="top")+
  scale_x_discrete(limit = c(8:18), labels = c("8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18"))
dev.off()
```


***Function versus content words***
```{r, echo=FALSE, message=FALSE, fig.width=10,fig.height=9}

R2_open_close=Linear_model_by_group(dat, c(13), c('TPs', 'PUDDLE', 'DiBs', 'AGu', 'gold'),c("syllable", "phoneme"), group1= "open_close", var_group1 = c("function", "content"))
R2_open_close_gold<-R2_open_close%>%filter(algo=="gold")
R2_open_close_algos<-R2_open_close%>%filter(algo %in% c('TPs', 'PUDDLE', 'DiBs', 'AGu'))

if (save==TRUE)
{png(paste(path_to_figures, "/R2_13mo_FunctionContent_nbtokens.png", sep=""),width=2500,height=2500, res=200 )}

ggplot(R2_open_close_algos, aes(x = algo, y = R2, fill=algo)) +
  geom_bar(position="dodge", stat="identity", show.legend=TRUE)+
  geom_abline(data=R2_open_close_gold, aes(slope=0, intercept=R2))+
  geom_text(data=R2_open_close_algos, aes(label=nbtokens), vjust=2, color="black", size=6)+
  facet_grid(group1 ~ unit)+
  theme_linedraw(base_size = 22)+
  scale_y_continuous(limits = c(0, 0.35))+
  theme(legend.position="top")+
  labs(title="", x="", y="Coefficient of determination R2")
dev.off()
```


***Mono verus polysyllabic words***
```{r, echo=FALSE, message=FALSE, fig.width=10,fig.height=9}
R2_length=Linear_model_by_group(dat, c(13), c('TPs', 'PUDDLE', 'AGu', 'gold', 'DiBs'),c("syllable", "phoneme"), group1= "length", var_group1 = c("M", "P") )
R2_length_gold<-R2_length%>%filter(algo=="gold")
R2_length_algos<-R2_length%>%filter(algo %in% c('TPs', 'PUDDLE', 'DiBs', 'AGu'))

if (save==TRUE)
{png(paste(path_to_figures, "/R2_13mo_MP_nbtokens.png", sep=""),width=2500,height=2500, res=200 )}

ggplot(R2_length_algos, aes(x = algo, y = R2, fill=algo)) +
  geom_bar(position="dodge", stat="identity",show.legend=TRUE)+
  geom_abline(data=R2_length_gold, aes(slope=0, intercept=R2))+
  geom_text(data=R2_length_algos, aes(label=nbtokens), vjust=-1, color="black", size=6)+
  facet_grid(group1 ~ unit)+
  theme_linedraw(base_size = 22)+
  scale_y_continuous(limits = c(0, 0.35))+
  theme(legend.position="top")+
  labs(title="", x="", y="Coefficient of determination R2")
dev.off()
# Note : DiBS with syllable has no polysyllabic words : R2=0 by default
```


***Interaction length open/close class ***
**** For TPs across ages ****
```{r}
R2=Linear_model_by_group(dat, c(8:18), c('TPs', 'PUDDLE', 'AGu', 'gold', 'DiBs'),c("syllable", "phoneme"), group1= "length", var_group1 = c("M", "P"),group2= "open_close", var_group2 = c("function", "content") )
```


```{r}
#R2=mean_R2_over_CDI_reports(d_comprehension, data_algo, 66, c(8:18), 10, c('TPs', 'PUDDLE', 'DiBs', 'AGu', 'gold'),c("syllable", "phoneme"))
```

```{r}
R2_g<-R2%>%filter(algo=="gold" )
R2_algos<-R2%>%filter(algo %in% c('TPs', 'PUDDLE', 'AGu', 'DiBs'))
R2_TP<-R2%>%filter(algo %in% c('TPs', 'gold'), unit=="syllable")

if (save==TRUE)
{png(paste(path_to_figures, "/R2_TPs_MP_FC_phoneme_syllable_nbtokens.png", sep=""),width=2500,height=2500, res=200 )}

ggplot(R2_TP, aes(x = age, y = R2, fill=algo)) +
  geom_bar(position="dodge", stat="identity")+
  #geom_abline(data=R2_g, aes(slope=0, intercept=R2))+
  facet_grid(group1 ~ group2)+
  #geom_text(data=R2_TP, aes(label=nbtokens), vjust=0, color="black", size=6, position = position_dodge(0.9))+
  theme_linedraw(base_size = 22)+
  scale_y_continuous(limits = c(0, 0.38))+
  theme(legend.position="top")+
  labs(title="", x="Age (month)", y="Coefficient of determination R2")+
  scale_x_discrete(limit = c(8:18), labels = c("8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18"))
dev.off()
```


***For all algo at one age ***
```{r}
R2=Linear_model_by_group(dat, c(13), c('TPs', 'PUDDLE', 'AGu', 'gold', 'DiBs'),c("syllable", "phoneme"), group1= "length", var_group1 = c("M", "P"),group2= "open_close", var_group2 = c("function", "content") )
R2_g<-R2%>%filter(algo=="gold" )
R2_algos<-R2%>%filter(algo %in% c('TPs', 'PUDDLE', 'AGu', 'DiBs'))
R2_TP<-R2%>%filter(algo %in% c('TPs', 'gold'), unit=="syllable")

if (save==TRUE)
{png(paste(path_to_figures, "/R2_13mo_MP_FC_phoneme_syllable_nbtokens.png", sep=""),width=2500,height=2500, res=200 )}

ggplot(R2_algos, aes(x = algo, y = R2, fill=unit)) +
  geom_bar(position="dodge", stat="identity")+
  geom_abline(data=R2_g, aes(slope=0, intercept=R2))+
  facet_grid(group1 ~ group2)+
  geom_text(data=R2_algos, aes(label=nbtokens), vjust=0, color="black", size=6, position = position_dodge(0.9))+
  theme_linedraw(base_size = 24)+
  scale_y_continuous(limits = c(0, 0.6))+
  theme(legend.position="top")+
  labs(title="", x="", y="Coefficient of determination R2")
dev.off()
```

***Lexical classes***
```{r, echo=FALSE, message=FALSE, fig.width=10,fig.height=9}
R2_lexclasses=Linear_model_by_group(dat, c(13), c('TPs', 'PUDDLE', 'DiBs', 'AGu', 'gold'),c("syllable", "phoneme"), group1= "lc", var_group1 = c("nouns", "adjectives", "verbs","exclamation", "adverbs", "prepositions", "pronouns", "determiners", "wh-"))

ggplot(R2_lexclasses, aes(x = algo, y = R2, fill=algo)) +
  geom_bar(position="dodge", stat="identity")+
  facet_grid(group1 ~ unit)
```

------

## Linear mixed effect model

***Model 0 : fixed effect of Frequency and random effect of algo and unit at 13 mo***
```{r}

fit_random_inter=lmer(prop ~ log(Freq) + (1|algos), dat_age_unit, REML = TRUE)
fit_random_slope=lmer(prop ~ log(Freq)  +(1+ log(Freq)|algos) ,dat_age_unit, REML = TRUE)
summary(fit_random_inter)
summary(fit_random_slope)
anova(fit_random_inter, fit_random_slope)
summary(anova(fit_random_inter, fit_random_slope))
```

***Model 1 : fixed effect of Frequency and random effect of algo and ages***
```{r}
fit_random_inter=lmer(prop ~ log(Freq) + (1|algos) + (1|age), dat_unit, REML = TRUE)
fit_random_slope=lmer(prop ~ log(Freq)  +(1+ log(Freq)|algos)+(1+ log(Freq)|age),dat_unit, REML = TRUE)
summary(fit_random_inter)
summary(fit_random_slope)
anova(fit_random_inter, fit_random_slope)
summary(anova(fit_random_inter, fit_random_slope))
```


**Comparing models**
```{r}

fit_length <- lmer(prop ~ log(Freq)+ +(1+log(Freq)|algos) + length , data=dat_age_unit, REML = TRUE)

fit_open_close<- lmer(prop ~ log(Freq) +(log(Freq)|algos) + open_close , data=dat_age_unit, REML = TRUE)

fit_total <- lmer(prop ~ log(Freq) +(log(Freq)|algos) + length + open_close, dat_age_unit, REML = TRUE)

summary(fit_length)
summary(fit_open_close)
summary(fit_total)
anova(fit_length,  fit_total)
```
